intro

### 2022-03-03 06_Paper/ER-ED/TheoreticalBackground.Rmd
changed numbers of Hs

* H1a) Subjective arousal (arousal ratings) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
* H1b) Physiological responses in facial EMG that is sensitive to negative emotion (*corrugator* activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
* H1c) Physiological responses in facial EMG that is sensitive to negative emotion (*levator* activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
* H2a) Subjective effort (effort ratings) is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
* H2b) The majority of participants re-uses the strategy that was least effortful for them.

@@

* H3a) Subjective effort ratings negatively predict SVs of ER strategies.
* H3b) Subjective arousal ratings negatively predict SVs of ER strategies.
* H3c) EMG *corrugator* activity negatively predicts SVs of ER strategies.
* H3d) EMG *levator* activity negatively predicts SVs of ER strategies.
* H4a) SVs decline with increasing effort, even after controlling for task performance measured by subjective arousal ratings, *corrugator* and *levator* activity.

@@

* H5a) The higher the SV, the more likely the respective strategy is chosen.
* H5b) SVs are lower and decline stronger when ER flexibility is lower.

>>>>

* H1a) Subjective arousal (arousal ratings) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
* H2a) Physiological responses in facial EMG that is sensitive to negative emotion (*corrugator* activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
* H2b) Physiological responses in facial EMG that is sensitive to negative emotion (*levator* activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
* H3a) Subjective effort (effort ratings) is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
* H3b) The majority of participants re-uses the strategy that was least effortful for them.

@@

* H4a) Subjective effort ratings negatively predict SVs of ER strategies.
* H4b) Subjective arousal ratings negatively predict SVs of ER strategies.
* H4c) EMG *corrugator* activity negatively predicts SVs of ER strategies.
* H4d) EMG *levator* activity negatively predicts SVs of ER strategies.
* H5a) SVs decline with increasing effort, even after controlling for task performance measured by subjective arousal ratings, *corrugator* and *levator* activity.

@@

* H6a) The higher the SV, the more likely the respective strategy is chosen.
* H6b) SVs are lower and decline stronger when ER flexibility is lower.
